\documentclass[a4paper,10pt,unnumberedsections,twoside]{LTJournalArticle}
% https://www.latextemplates.com/template/journal-article
% To add a 2 columns span environment, add * to the environment name (figure*, table*, etc.)

\usepackage{float}
\usepackage{background}
\backgroundsetup{
  color=gray,
  opacity=0.2,
  contents=Preliminary
}

\hypersetup{
pdftitle={ME738 - Special Topics in Materials},
pdfsubject={Project report},
pdfauthor={Tommaso Bocchietti}
}

\addbibresource{references.bib}

\runninghead{Chip Scale Atomic Clocks Sources}

\footertext{ME738 - Special Topics in Materials}

\setcounter{page}{1}

\title{Chip Scale Atomic Clocks Sources:\\Working Principles and Applications}

\author{
	Tommaso Bocchietti\textsuperscript{1,2}\thanks{\textbf{Final revision:} April ??, 2024}
}

\date{\footnotesize
\textsuperscript{\textbf{1}}Department of Mechanical \& Mechatronics Engineering, University of Waterloo\\
\textsuperscript{\textbf{2}}Dipartimento di Meccanica, Politecnico di Milano
}

\renewcommand{\maketitlehookd}{
	\begin{abstract}

		Chip Scale Atomic Clocks (CSACs) have emerged as compact and high-performance timing references, revolutionizing various applications where precise timekeeping is essential.
		This paper provides a comprehensive overview of the working principles and diverse applications of CSACs.
		Beginning with an introduction to the fundamental principles of atomic clocks, including the operation of the cesium and rubidium-based systems, this paper delves into the miniaturization and integration of these technologies onto semiconductor chips.

		The discussion elaborates on the core components of CSACs, such as the miniature atomic vapor cell, laser systems for atomic excitation, and the interrogation and control electronics.
		The exceptional stability and accuracy of CSACs, often surpassing traditional quartz crystal oscillators, make them ideal for applications requiring precise timekeeping in challenging environments.
		These clocks exhibit long-term frequency stability on the order of parts per billion over extended periods, enhancing their utility in critical infrastructure, communication systems, aerospace, and defense applications.

		Moreover, the compact size and low power consumption of CSACs enable their integration into a wide array of devices, including unmanned aerial vehicles (UAVs), satellites, and portable communication equipment.
		This paper explores specific use cases, such as satellite navigation systems where CSACs enhance Global Navigation Satellite System (GNSS) signals' accuracy and integrity.
		Furthermore, CSACs find applications in financial networks, where high-frequency trading relies on nanosecond-level precision.

		In conclusion, the paper highlights the burgeoning role of Chip Scale Atomic Clocks in modern technology landscapes.
		Their miniature size, exceptional performance, and versatility make them pivotal in advancing fields requiring precise synchronization and timekeeping.
		As research continues to refine these systems, the potential for further integration into emerging technologies such as Internet of Things (IoT) devices and 5G networks becomes increasingly promising.

	\end{abstract}
}

\begin{document}

\maketitle

% Why rubidium? https://physics.stackexchange.com/questions/726071/why-rubidium-87-instead-of-rubidium-85-for-atomic-clocks
% Interest patent: https://patents.google.com/patent/US6320472B1/en

\input{src/01 - introduction}
\input{src/02 - working_principles}
% \input{src/03 - applications}
% \input{src/04 - conclusion}

% \section*{Acknowledgments}

\printbibliography

\end{document}
