\section{Results}
\label{sec:results}

The \acrshort{scgs} algorithm has been implemented in \texttt{C} and tested on a simple 2D lid-driven cavity flow problem.

In the following we are going to compare the results obtained using our code with the ones reported in Ghia et al. \cite{Ghia1982HighReSF}.

\textbf{
    Note: we will see that our code has some issues related to convergence and stability.
    This affect the under-relaxation factors required to stabilize the solution that have to be decreased to very low values (e.g. $\alpha_u = 0.01$ and $\alpha_v = 0.01$ or less).
    This is not a good practice and it's not a solution to the problem. We are currently investigating the issue and we will update the codebase as soon as possible.
}

\input{src/07.1 - ghia_exact_solution}
\input{src/07.2 - comparison_with_ghia}
\input{src/07.3 - solution_07}
\input{src/07.4 - convergence_analysis}


\subsection{Final remarks}

As we have seen, our code has some issues related to convergence and stability.

In particular, in order to have a convergent solution, we have to decrease the under-relaxation factors to very low values (e.g. $\alpha_u = 0.01$ and $\alpha_v = 0.01$ or less).

By debugging through the code, we can clearly see that this is due to the low or absent diagonal dominance of the coefficient matrix (Vanka's matrix).

Moreover, by deepening the problem, we have found that the convergence of the algorithm is ensured only if the following condition is satisfied:

\begin{equation}
    |a_{ii}| \geq \sum_{j \neq i} |a_{ij}| \quad \forall i = 1, 2, 3, 4
    \label{eq:diagonal_dominance}
\end{equation}

Where $a_{ij}$ are the elements of the coefficient matrix.

In the \acrshort{scgs} algorithm the coefficient matrix is in the form of Equation \ref{eq:vanka_matrix}, so we can states that the diagonal dominance is ensured only if the following condition is satisfied:

\begin{equation}
    |a_{ii}| \geq |a_{5i}| \quad \forall i = 1, 2, 3, 4
\end{equation}

For how the system has been constructed, we know that:

\begin{align}
    a_{ii} & = f(\nu, \alpha_u, \alpha_v) \\
    a_{5i} & = f(Nx, Ny)
\end{align}

Where $f$ indicate a generic function.

Based on the equations and derivations done in the previous sections, we have that diagonal dominance is compromised when:

\begin{itemize}
    \item The grid is not fine enough (i.e. $Nx$ and $Ny$ are low) $\Rightarrow a_{5i} = \text{Cell sixe}$ is high
    \item The under-relaxation factors are high $\Rightarrow a_{ii} = A_p^\phi / \alpha_\phi$ is low
    \item The viscosity is low $\Rightarrow$ Diffusion term is low $\Rightarrow a_{ii}$ is low
\end{itemize}

When Equation \ref{eq:diagonal_dominance} is not satisfied once, then the algorithm will diverge imposing too high corrections to the state variables, causing the Convective terms to become too high at the next iteration (or neighboring cells).

\vspace{1em}

\textbf{Note: we know this should not append, but as of today we still haven't found the problem in our code.}

