\documentclass[titlesec]{araproposal}

\newcommand{\semph}[1]{\textbf{\textit{#1}}}
\newcommand{\para}[1]{\textbf{#1.}\ }

\hypersetup{
    pdftitle={ME663 - Computational Fluid Dynamics},
    pdfsubject={Proposal for research project},
    pdfauthor={Tommaso Bocchietti}
}
\bibliographystyle{abbrv}

\title{Designing an Ammonia-compatible Fuel Injector for retrofitting current Internal Combustion Engines using CFD}
\piauthor{Tommaso Bocchietti, Department of Mechanical \& Mechatronics Engineering, University of Waterloo}
% \copiauthorB{Co-PI Name, Title, Department Name, University Name}
\contact{Tommaso Bocchietti, \email{tbocchie@uwaterloo.ca}}
\date{March 20, 2024}

\begin{document}

\maketitle

\abstract{
    The continuous emission of greenhouse gases from internal combustion engines is a major concern for the environment.
    The transportation sector is the second-largest source of greenhouse gas emissions in the world, preceded only by the energy sector.

    In the past few years, some alternative to fossil fuel have been proposed, such as the adoption of electric vehicles, the use of methane, or the use of hydrogen.
    However, all of these alternatives have some drawbacks, such as the needs of a huge infrastructure to support the use of electric vehicles, or the high emissions of $\mathrm{CO_2}$ from methane combustion, or the low energy density of gaseous hydrogen.

    Ammonia instead is a promising alternative fuel, with a considerable energy density and no $\mathrm{CO_2}$ emissions.
    However, the use of ammonia requires the development of new mechanical components that can handle its specific properties.

    This research project aims to develop a new fuel injector suitable for ammonia, so that it can be retrofitted in existing Internal Combustion Engines (ICEs).
    The project will use Computational Fluid Dynamics (CFD) simulations to model the spray of Ammonia inside the combustion chamber, giving insights on the design of the new fuel injector.
}

\keywords{Ammonia, Fuel Injector Design, Internal Combustion Engines, Computational Fluid Dynamics}

\input{src/01 - objectives_and_impact}
\input{src/02 - background}
\input{src/03 - research_plan_and_methodology}
\input{src/04 - deliverables}

\appendix

% \newpage
\bibliography{references}

\end{document}


