\section{Outline}
\label{sec:outline}

We leave here a general outline that will be used as a guide for the development of the project.

\begin{enumerate}
    \item Introduction: Discuss the need for precise timekeeping and the exigence of chip-scale atomic clocks.

    \item Engineering of Chip-Scale Atomic Clocks: Discuss the principles of operation and the advantages/disadvantages of each type. Possibility to use simulation tools such as \texttt{COMSOL Multiphysics} to visualize the principles of operation of these devices (based on the time available and the complexity of the simulation and the software).

    \item Technology Comparison: Introduce the different types of chip-scale atomic clocks, such as rubidium and cesium-based devices. Compare and contrast the different chip-scale atomic clock technologies in terms of size, power consumption, accuracy, and suitability for various applications.

          % \item Fabrication and Manufacturing: Explore the components of chip-scale atomic clocks such as atomic vapor cells, laser systems, and control electronics. Understand the microfabrication techniques used in their manufacturing.

    \item Applications: Investigate the diverse applications of chip-scale atomic clocks, ranging from aerospace and defense to telecommunications and scientific research.

    \item Challenges and Future Directions: Identify current challenges such as size reduction and power efficiency, and consider future trends like adoption of optical lattice clocks and integration with quantum technologies.

    \item Conclusion: Summarize the key findings of the research and discuss the implications for future advancements and applications of chip-scale atomic clocks.
\end{enumerate}

In case of time availability, we will also cover the Fabrication and Manufacturing of these devices, understanding the microfabrication techniques used in their manufacturing.

In general, given a time constraint of 4/5 weeks, the project will be divided as follows (tentative)

\begin{itemize}
    \item Week 1: Introduction + Engineering of Chip-Scale Atomic Clocks
    \item Week 2: Engineering of Chip-Scale Atomic Clocks (possible simulation and results analysis)
    \item Week 3: Technology Comparison + Applications
    \item Week 4: Challenges and Future Directions + Conclusion
    \item Week 5: Final report writing
\end{itemize}
